### 2015-05-14 intro.tex
fixes

In this paper, we present \whoop, a new fully automatic approach that statically analyzes device drivers written in C for data races. \whoop is empowered by \emph{symbolic pairwise lockset analysis}, a novel technique for verifying the absence of data races in device drivers. We attempt to prove a driver race-free by: (i) deriving a sound \emph{sequential} program that \emph{over-approximates} the originally concurrent program; (ii) instrumenting it to record \emph{locksets}; and (iii) using the locksets to assert that all accesses to the same shared resource are \emph{consistently} protected by at least one common lock. Reducing analysis to reasoning over a sequential program avoids the need to enumerate thread interleavings, and allows reuse of existing successful sequential verification techniques.
%
We then show that by exploiting the race-freedom guarantees provided by our symbolic analysis we can achieve a sound partial-order reduction that significantly accelerates \corral~\cite{lal2012corral}, a state-of-the-art precise bug-finder used by Microsoft to analyze drivers, as well as other concurrent programs. Using \whoop and \corral we analyzed \sizeOfBenchmarks drivers from the 4.0 Linux kernel distribution.  We find that by combining \whoop and \corral we achieve concurrency analysis speedups in the range of 1.5--10$\times$ for most of our benchmarks, compared with using \corral in isolation.  For two drivers, we observe even greater speedups of 12$\times$ and 20$\times$.

>>>>

In this paper, we present \whoop, a new fully automatic approach that statically analyzes device drivers written in C for data races. \whoop is empowered by \emph{symbolic pairwise lockset analysis}, a novel technique for verifying the absence of data races in device drivers. We attempt to prove a driver race-free by: (i) deriving a sound \emph{sequential} program that \emph{over-approximates} the originally concurrent program; (ii) instrumenting it to record \emph{locksets}; and (iii) using the locksets to assert that all accesses to the same shared resource are \emph{consistently} protected by at least one common lock. Reducing analysis to reasoning over a sequential program avoids the need to enumerate thread interleavings, and allows reuse of existing successful sequential verification techniques.
%
We then show that by exploiting the race-freedom guarantees provided by our symbolic analysis we can achieve a sound partial-order reduction that significantly accelerates \corral~\cite{lal2012corral}, a state-of-the-art precise bug-finder used by Microsoft to analyze drivers, as well as other concurrent programs. Using \whoop and \corral we analyzed \sizeOfBenchmarks drivers from the 4.0 Linux kernel distribution.  We found that by combining \whoop and \corral we achieve can concurrency analysis speedups in the range of 1.5--10$\times$ for most of our benchmarks, compared with using \corral in isolation.  For two drivers, we observed even greater speedups of 12$\times$ and 20$\times$.
